\pagenumbering{arabic}
\par
Significance of Artificial intelligence is increasing in the day to day life. Natural language processing is an important component of artificial intelligence. Natural Language Processing is an area of research and application that explores how computers can be used to understand and manipulate natural language text or speech to do useful things. Applications of NLP include a number of fields of studies, such as machine translation, natural language text processing and summarization, user interfaces, multilingual and cross language information retrieval (CLIR), speech recognition, artificial intelligence and expert systems, and so on. The technology that is going to rule the next generation is the text processing.
\par
The aim of this project is to collect the data that is spread across the web, and process in a better way, which can be used for updating knowledge of the mankind. In this project we are implementing a system, which keep track of the technology and market trends around the globe.
This comes under a broader view of Internet of Things. 
\par
We have built the system to accommodate two kinds of users, the corporate user and the naïve user. At the completion of this project we have managed to provide a website, through which the user can locate technology companies based on locations, their field of expertise. In this web portal, users can also find different companies sharing same geographic location and technology areas they are engaged in. We are also providing a website in which user can walk through the technology related articles.
\par
Market Intelligence using graph database project involves four modules. These modules are Data extractor module, NLP module, Middleware module, Frontend module. The data is spread across the web. In order to collect this data, we created the Data extractor module. The data of our interest are collected from RSS field. We have used Crunchbase API, Discovery API, Boilerpipe API, AngelList API for initial database creation and data extraction.
\par
In the Natural language processing module, we extract the relations and keywords from the data that we have collected from the web using our extraction module. We have used Alchemy API for relation and keyword extraction. The keywords used for processing are launch, announcement, merging, invest, introduce, patent, appoint, hire etc. The output of the NLP module is used for tagging articles.
\par
The next module that is the middleware module operate on the output from the previous module.
In this module, we check whether the data that we have extracted satisfies out grammar constraints. Any data that does not match any constraints are excluded. If it matches any of the constraint, it will be sent to the admin for validation. Another task of this module, is to avoid certain entities so that we are able to represent only the required ones in the graph. 
\par
The frontend module is another important module in this project. Our frontend module conforms to the golden rules of user interface design. We have created two websites, one for the user to query and the other one for displaying technology articles. In the user website, we provide the privilege for the user to create queries of his needs and query in our database. By enabling this feature, we have manages to put the user in control. The output of the query is displayed using graph. To realize this, we make use of the D3 visualization library. During the development of all these modules, we have managed to conform to industry standards.
\par
The project aims at redefining the way the knowledge is made available for the common and corporate people, in a much convenient and easier to access way. We have tried at our level best in making sure that only legit information is made available to the users.
